---
title: "ggplot2_hook"
author: "Treasure"
date: "2023-02-28"
output:
  pdf_document: default
  html_document: default
---

## Setting up my environment
Notes: setting up my environment by loading the 'tidyverse' and 'palmerpenguin' packages.

```{r loading packages}
library("tidyverse")
library("palmerpenguins")
```

## Visualizations
Here, we will go through a series of visualizations.

## Flipper and body masin purple
Here, we plot flipper length against body ass

```{r}
ggplot(data=penguins, aes(x =flipper_length_mm, y=body_mass_g))+
  geom_point(color="purple")
```

### Flipper and body mass by species
Here, we plot flipper length against body mass and look at the breakdown by species

```{r}
ggplot(data=penguins, aes(x =flipper_length_mm, y=body_mass_g))+
  geom_point(aes(shape=species))
```

### Flipper and body mass by species and sex

Here, we plot flipper lrngth against body mass and look at the breakdown by species and sex
```{r}
ggplot(data=penguins, aes(x =flipper_length_mm, y=body_mass_g))+
  geom_point(aes(shape=species,
                 color=species))+
  facet_wrap(~sex)
```

